Classification and Regression on Random Dot Product Graphs

### 2024-01-26 draft.Rmd
found issues with proofs--working on fixing them

\begin{theorem}[Consistency of algorithm \ref{alg:bezier-fit}]
\label{thm:bezier-consistency}
Suppose $A \sim \LSM(p, F_\theta)$ such that $p : [0, 1] \to \mathbb{R}^d$ is a Bezier polynomial of degree $R$ with coefficients $b$, and $F_\theta$ is a probability distribution with probability density function $f_\theta(t)$ that is absolutely continuous on support $[0, 1]$ and $\min_t f_\theta(t) > 0$ $\forall t \in [0, 1]$. 
Let $\hat{T}$ and $\hat{b}$ be the minimizers of the loss function in equation \ref{eq:bezier-ls} from $A$. 
Then as $n \to \infty$, $\|T - \hat{T}\|_{2, \infty} \stackrel{p}{\to} 0$ where $T$ is defined as in equation \ref{eq:bezier-loss}, and $\|b - \hat{b} W \|_F \stackrel{p}{\to} 0$ for some $W \in \mathbb{O}(d)$.
\end{theorem}

\begin{proof}
By lemma \ref{lem:bezier-consistency}, $\|T b - \hat{T} \hat{b} W\|_{2,\infty} \stackrel{p}{\to} 0$ as $n \to \infty$. 
Then

$$
\begin{aligned}
\|T b - \hat{T} \hat{b} W\|_{2,\infty} & = \|T b - \hat{T} \hat{b} W + \hat{T} b - \hat{T} b\|_{2,\infty} \\
& = \|(T - \hat{T}) b - \hat{T} (\hat{b} W - b)\|_{2,\infty} \\
& \leq \|(T - \hat{T}) b\|_{2,\infty} + \|\hat{T} (\hat{b} W - b)\|_{2,\infty} \\
& \leq \|T - \hat{T}\|_{2,\infty} \|b\|_F + \|\hat{T}\|_{2,\infty} \|b - \hat{b} W\|_F \\
& \stackrel{p}{\to} 0.
\end{aligned}
$$
$\|b\|_F$ and $\|\hat{T}\|_{2,\infty}$ are finite, so both $\|T - \hat{T}\|_{2,\infty}$ and $\|b - \hat{b} W\|_F$ must converge to $0$ in probability. 
\end{proof}

@@

>>>>

\begin{lemma}
Suppose $A \sim \LSM(p, F_\theta)$ such that $p : [0, 1] \to \mathbb{R}^d$ is a Bezier polynomial of degree $R$ with coefficients $b$, and $F_\theta$ is a probability distribution with probability density function $f_\theta(t)$ that is absolutely continuous on support $[0, 1]$ and $\min_t f_\theta(t) > 0$ $\forall t \in [0, 1]$. 
Let $\hat{T}$ and $\hat{b}$ be the minimizers of the loss function in equation \ref{eq:bezier-ls} from $A$. 
Then $\|T - \hat{T}\|_{2, \infty} \stackrel{p}{\to} 0$ as if and only if $\|b - \hat{b} W\|_F \stackrel{p}{\to} 0$. 
\end{lemma}

\begin{theorem}[Consistency of algorithm \ref{alg:bezier-fit}]
\label{thm:bezier-consistency}
Suppose $A \sim \LSM(p, F_\theta)$ such that $p : [0, 1] \to \mathbb{R}^d$ is a Bezier polynomial of degree $R$ with finite coefficients $b$, and $F_\theta$ is a probability distribution with probability density function $f_\theta(t)$ that is absolutely continuous on support $[0, 1]$ and $\min_t f_\theta(t) > 0$ $\forall t \in [0, 1]$. 
Let $\hat{T}$ and $\hat{b}$ be the minimizers of the loss function in equation \ref{eq:bezier-ls} from $A$. 
Then as $n \to \infty$, $\|T - \hat{T}\|_{2, \infty} \stackrel{p}{\to} 0$ where $T$ is defined as in equation \ref{eq:bezier-loss}, and $\|b - \hat{b} W \|_F \stackrel{p}{\to} 0$ for some $W \in \mathbb{O}(d)$.
\end{theorem}

\begin{proof}

\end{proof}

@@

\begin{proof}
By theorem \ref{thm:bezier-consistency}, 
\end{proof}
